---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/expersso/csp.svg?branch=master)](https://travis-ci.org/expersso/csp)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/csp)](https://cran.r-project.org/package=csp)
[![CRAN_Logs_Badge](http://cranlogs.r-pkg.org/badges/grand-total/csp)](https://cran.r-project.org/package=csp)

## Introduction

This package contains the [Correlates of State
Policy](http://ippsr.msu.edu/public-policy/correlates-state-policy) 
dataset, which

> ... includes more than seven-hundred variables, with observations across the
> U.S. 50 > states and time (1900 – 2016). These variables represent policy
> outputs or > political, social, or economic factors that may influence policy
> differences > across the states. The codebook includes the variable name, a
> short description > of the variable, the variable time frame, a longer
> description of the variable, > and the variable source(s) and notes.

See website above for suggested citation.

The package allows the user to load and work with the dataset using the R 
programming language. Crucially, it incorporates the entire codebook into the
dataset, which allows for easier filtering, finding units and sources, etc.

## Example use

```{r, warning=FALSE, message=FALSE}
library(csp)
library(ggplot2)

data(csp, package = "csp")
dim(csp)
names(csp)
csp[1:2, ]
```

```{r, fig.width = 6, fig.height = 4, warning=FALSE, message=FALSE}
df <- subset(csp, variable == "real2_pc_inc_quar")
df$value <- as.numeric(df$value)

ggplot(df, aes(x = year, y = value, color = state)) +
  geom_line(show.legend = FALSE) +
  scale_color_grey() +
  theme_light() +
  labs(x = NULL, y = NULL,
       title = df$var_desc[1],
       subtitle = df$var_long_desc[1])
```

## Disclaimer

This package is not affiliated with, nor endorsed by, the Correlates of State
Policy Project. All credit go to the original authors, and questions should be
directed to them. Please check the [official website](http://ippsr.msu.edu/public-policy/correlates-state-policy) 
for further details on citations, etc.