---
title: "csp: Correlates of State Policy Dataset in R"
author: "Eric Persson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{csp}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

This package contains the [Correlates of State
Policy](http://http://ippsr.msu.edu/public-policy/correlates-state-policy) 
dataset, which

> ... includes more than seven-hundred variables, with observations across the
> U.S. 50 > states and time (1900 – 2016). These variables represent policy
> outputs or > political, social, or economic factors that may influence policy
> differences > across the states. The codebook includes the variable name, a
> short description > of the variable, the variable time frame, a longer
> description of the variable, > and the variable source(s) and notes.

Suggested citation: 

> Jordan, Marty P. and Matt Grossmann. 2016. The Correlates of State Policy
> Project v.1.0. East Lansing, MI: Institute for Public Policy and Social Research
> (IPPSR).

The package allows the user to load and work with the dataset using the R
programming language.

## Example use

```{r, warning=FALSE, message=FALSE}
library(csp)
library(ggplot2)

data(csp, package = "csp")
dim(csp)
names(csp)
csp[1:2, ]
```

```{r, fig.width = 6, fig.height = 4, warning=FALSE, message=FALSE}
df <- subset(csp, variable == "real2_pc_inc_quar")
df$value <- as.numeric(df$value)

ggplot(df, aes(x = year, y = value, color = state)) +
  geom_line(show.legend = FALSE) +
  scale_color_grey() +
  theme_light() +
  labs(x = NULL, y = NULL,
       title = df$var_desc[1],
       subtitle = df$var_long_desc[1])
```

## Disclaimer

This package is not affiliated with, nor endorsed by, the Correlates of State
Policy Project. All credit go to the original authors, and questions should be
directed to them. Please check the [official website](http://http://ippsr.msu.edu/public-policy/correlates-state-policy) 
for further details on citations, etc.